%Custom Functions
\newcommand{\CompanyName}{TT} % update later

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

\usepackage{pdflscape}

\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{lastpage}

% Please add the following required packages to your document preamble:
\usepackage{multirow}
\usepackage[numbers]{natbib}

\usepackage{listings}
\usepackage{hyperref}
\usepackage{amsmath}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
	urlcolor=cyan
}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=single,
  language=C++,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers = none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true
}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\fancypagestyle{fancylandscape}{
\fancyhf{} %Clears the header/footer
\fancyfoot{% Footer
\makebox[\textwidth][r]{% Right
  \rlap{\hspace{.75cm}% Push out of margin by \footskip
    \smash{% Remove vertical height
      \raisebox{4.87in}{% Raise vertically
        \rotatebox{90}{Page \thepage\ of \pageref{LastPage}}}}}}}% Rotate counter-clockwise
\renewcommand{\headrulewidth}{0pt}% No header rule
\renewcommand{\footrulewidth}{0pt}% No footer rule
}

\pagestyle{fancyplain}
\fancyhf{}
\fancyfoot[c]{Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

	\title{VisualPro - Proposal}

	\author{\IEEEauthorblockN{1\textsuperscript{st} Given Edward Patch}
	\IEEEauthorblockA{\textit{Software Engineer Student (of BSc Year 3)} \\
    \textit{Independent Project}\\
    \textit{University of Wales Trinity St. Davids (of Mike Dacey)}\\
    Swansea, Wales \\
    Student ID: 1801492}}

     \maketitle
    
    \thispagestyle{plain}
    \pagestyle{plain}
    
    \tableofcontents
	  \vspace{.5cm}
    %\newpage
    \begin{abstract}
      Documentation provides technical information to use the Programming Planner library. Technical information includes examples of executions and briefs the developer on using the library effectively.
    \end{abstract}

    \begin{IEEEkeywords}
        Documentation, Programming Planner, Development
    \end{IEEEkeywords}

    \section{Introduction}
      Programming Planner generates different languages based on the user input. A provided Extensible Markup Language (XML) file, available on the VisualPro's GitHub Repository~\href{#}{Add Link}. The documentation guides the developer of ways to import and call the Programming Planner's Dynamic-Link Library (DLL) packages with explanations of DLL injection points and displays a series of examples of the Programming Planner's capabilities.

    \section{Importing the Library}
      Libraries are available for each language—explaining how to connect to Programming Planner's DLL packages. A web link with example code is attached to understand how a DLL library loads into each language listed. It is essential to mention that DLL files will not work on a Linux system, and a Shared Object (SO) library is unavailable. If the language is not displayed in the list below, then search on a Search Engine `How to import a DLL file in \textit{languageName}'. The code block below shows a communication example with two functions; The first function displays the string `C++ says Helloworld', and the second function enables addition and subtraction from two numbers to support the examples in the following segments.

      \begin{lstlisting}
        extern "C" _declspec(dllexport) const char* Helloworld();

        // opt == true(Addition) and opt == false(Subtraction) 
        extern "C" _declspec(dllexport) double Calculator(double x, double y, bool opt);
      \end{lstlisting}
      \subsection{Language: C++}
        One method to import a DLL library in C++ is to import the `windows.h' and `tchar.h' libraries. To load the DLL library, the macro \textit{LoadLibrary} and \textit{GetProcAddress} function found in `windows.h' include is required. The `tchar.h' library casts a \textit{const char*} datatype to a \textit{unicode} format. \textit{FreeLibrary} closes the DLL library and clears the memory from the `dll' variable name.
        \begin{lstlisting}
          #include <iostream>
          #include <windows.h>
          #include <tchar.h>
          typedef const char* (*Helloworld_t)();
          typedef double (*Calculator_t)(double x, double y, bool opt);

          int main() {
            auto dll = LoadLibrary(
              _T("DLL_Library.dll"));
            auto helloworld = (Helloworld_t)GetProcAddress(dll, "Helloworld");
            auto calculator = (Calculator_t)GetProcAddress(dll, "Calculator");

            if(dll) {
              std::cout << helloworld() << "\n";
              std::cout << "Add: " << calculator(7, 3, true) << " | Subtraction: " << calculator(7, 3, false);
            } else std::cout << "Not Found";

            FreeLibrary(dll);
            return 0;  
          }
        \end{lstlisting}
      \subsection{Language: C\#}
      \subsection{Language: Java}
      \subsection{Language: NodeJS}

    \section{Communications}

    \section{Library Examples}

    \section{Terminology}
      List of terminologies used in this document:-
      \begin{itemize}
        \item XML - Extensible Markup Language.
        \item DLL - Dynamic-Link Library.
        \item SO - Shared Object.
        \item IDE - Integrated Development Environment.
      \end{itemize}

  \nocite{*}
	\renewcommand\refname{\section{Reference List}}
	\small{\bibliographystyle{IEEEtran}
    \bibliography{ref}}
\end{document}