%Custom Functions
\newcommand{\CompanyName}{TT} % update later

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
%\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

\usepackage{pdflscape}

\usepackage[utf8]{inputenc}
\usepackage{fancyhdr}
\usepackage{lastpage}

% Please add the following required packages to your document preamble:
\usepackage{multirow}
\usepackage[numbers]{natbib}

\usepackage{listings}
\usepackage{hyperref}
\usepackage{amsmath}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    filecolor=magenta,      
	urlcolor=cyan
}

\usepackage{listings}
\usepackage{color}

\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}

\lstset{frame=single,
  language=C++,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\small\ttfamily},
  numbers = none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=true,
  tabsize=2
}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\fancypagestyle{fancylandscape}{
\fancyhf{} %Clears the header/footer
\fancyfoot{% Footer
\makebox[\textwidth][r]{% Right
  \rlap{\hspace{.75cm}% Push out of margin by \footskip
    \smash{% Remove vertical height
      \raisebox{4.87in}{% Raise vertically
        \rotatebox{90}{Page \thepage\ of \pageref{LastPage}}}}}}}% Rotate counter-clockwise
\renewcommand{\headrulewidth}{0pt}% No header rule
\renewcommand{\footrulewidth}{0pt}% No footer rule
}

\pagestyle{fancyplain}
\fancyhf{}
\fancyfoot[c]{Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}

\begin{document}

	\title{VisualPro - Research Proposal}

	\author{\IEEEauthorblockN{1\textsuperscript{st} Given Edward Patch}
	\IEEEauthorblockA{\textit{Software Engineer Student (of BSc Year 3)} \\
    \textit{Independent Project}\\
    \textit{University of Wales Trinity St. Davids (of Mike Dacey)}\\
    Swansea, Wales \\
    Student ID: 1801492}}

     \maketitle
    
    \thispagestyle{plain}
    \pagestyle{plain}
    
    \tableofcontents
	  \vspace{.5cm}
    %\newpage
	
    \begin{abstract}
      This document provides the proposal of the Independent Project. After doing in-depth research and planning, the working title for this project is VisualPro.
    \end{abstract}

    \begin{IEEEkeywords}
        Visual Programming, Proposal, Research.
    \end{IEEEkeywords}
  
    \section{Introduction}
      The VisualPro Proposal document includes a Literature Review, Aims and Objective, Project Design, Resources and Planning and Reference List.

      The Literature Review section includes academic books and journals related to the project proposal. Within the extensive research, hand-picked articles and journals to show what technologies are required to make the idea plausible, which in turn narrows down the association of the project towards the author's study area.
      
      After the Literature Review section, the Aims and Objectives of the project are covered. This section will give the reader an idea of how the final product will impact society and its user base.
    \section{Literature Review}

    \section{Aims and Objectives}
      \subsection{Aims}
      
      \subsection{Objectives}

    \section{Project Design}
      \subsection{Outline of Project Process}
      \subsection{Data Collection}
      \subsection{Risks and Limitations}
      \subsection{Ethical Issues}
    \section{Resources and Planning}
      \subsection{Resources Required}
        \textbf{Physical Resources}

        \textbf{Human Resources}

        \textbf{Other Resources}
      \subsection{Planning Chart}
        After planning the time schedule to 400 hours to fit in the 28$^{\text{th}}$ of April 2022 deadline. The time schedule finishes on the 12${\text{th}}$ of March 2022, giving leighway.~\href{https://view.monday.com/1722876472-ab76699feb1263e51a11f4bdf7fda63e?r=use1}{Time Schedule} - \\\url{https://view.monday.com/1722876472-ab76699feb1263e51a11f4bdf7fda63e?r=use1}
	\nocite{*}
	\renewcommand\refname{\section{Reference List}}
	\small{\bibliographystyle{IEEEtran}
    \bibliography{ref}}
\end{document}